Experiment 3 of 4

### 2016-09-27 experiments/e3/writeup/preprocessing/preprocessing.Rmd
pruned some columns from the data for e3 for upload to pure

# save dd as data.Rda
# This data set non-impossible trials and renamed/recomputed variables
write.table(dd, file="../data.txt")
```

>>>>

# save dd as data.Rda
# This data set non-impossible trials and renamed/recomputed variables
dd2 <- subset(dd, select=c(Subject, Trial, Item, c_Itm, Vagueness, c_Vag, Selection, c_Sel, Instruction, Order, Quantity, RT, RT_log, switchResponse))
write.table(dd2, file="../data.txt")
```
